\textbf{Unshuffling Permutations}

### 2016-04-07 slides/slides.tex
New example

  \onslide<2->
  \begin{exampleblock}{Example}
    The permutation $\pi := 183927B5C6A4$ is a square since it admits the
    perfect matching
    \begin{equation*}
    \begin{split}
    \begin{tikzpicture}[scale=0.35,inner sep=2pt,node distance=1cm]
        \tikzstyle{Vertex}=[draw,circle,minimum size=.45cm,font=\footnotesize]
        \draw node[Vertex,fill=RoyalBlue!30](U01){$1$};
        \draw node[Vertex,fill=RoyalBlue!30,right of=U01](U02){$8$};
        \draw node[Vertex,fill=BrickRed!30,right of=U02](U03){$3$};
        \draw node[Vertex,fill=RoyalBlue!30,right of=U03](U04){$9$};
        \draw node[Vertex,fill=RoyalBlue!30,right of=U04](U05){$2$};
        \draw node [Vertex,fill=BrickRed!30,right of=U05](U06){$7$};
        \draw node [Vertex,fill=BrickRed!30,right of=U06](U07){$B$};
        \draw node [Vertex,fill=BrickRed!30,right of=U07](U08){$5$};
        \draw node [Vertex,fill=BrickRed!30,right of=U08](U09){$C$};
        \draw node [Vertex,fill=BrickRed!30,right of=U09](U10){$6$};
        \draw node [Vertex,fill=RoyalBlue!30,right of=U10](U11){$A$};
        \draw node [Vertex,fill=RoyalBlue!30,right of=U11](U12){$4$};
        \draw [thick,->,>=latex']
        (U01.north) .. controls ($ (U01.north) + (0,2.25) $)
            and ($ (U03.north) + (0,2.25) $) .. (U03.north);
        \draw [thick,->,>=latex']
        (U02.south) .. controls ($ (U02.south) + (0,-2.25) $)
            and ($ (U06.south) + (0,-2.25) $) .. (U06.south);
        \draw [thick,->,>=latex']
        (U04.north) .. controls ($ (U04.north) + (0,2.5) $)
            and ($ (U07.north) + (0,2.5) $) .. (U07.north);
        \draw [thick,->,>=latex']
        (U05.south) .. controls ($ (U05.south) + (0,-2.5) $)
            and ($ (U08.south) + (0,-2.5) $) .. (U08.south);
        \draw [thick,->,>=latex']
        (U11.north) .. controls ($ (U11.north) + (0,2.5) $)
            and ($ (U09.north) + (0,2.5) $) .. (U09.north);
        \draw [thick,->,>=latex']
        (U12.north) .. controls ($ (U12.north) + (0,2.5) $)
            and ($ (U10.north) + (0,2.5) $) .. (U10.north);
    \end{tikzpicture}
    \end{split}
    \end{equation*}
    satisfying $\mathbf{P_1}$ and~$\mathbf{P_2}$.
    \smallskip

    Moreover, this shows that $\pi$ appears in the shuffle of the
    words $\textcolor{RoyalBlue}{1892A4}$ and
    $\textcolor{BrickRed}{37B5C6}$, both order isomorphic to
    $145263$.
  \end{exampleblock}
\end{frame}

>>>>

  \onslide<2->
  \begin{exampleblock}{Example}
    The permutation $\pi := 35867241$ is a square since it admits the
    perfect matching
    \begin{equation*}
    \begin{split}
    \begin{tikzpicture}[scale=0.35,inner sep=2pt,node distance=1cm]
        \tikzstyle{Vertex}=[draw,circle,minimum size=.45cm,font=\footnotesize]
        \draw node[Vertex,fill=RoyalBlue!30](U01){$(3, 1)$};
        \draw node[Vertex,fill=BrickRed!30,right of=U01](U02){$(5, 2)$};
        \draw node[Vertex,fill=BrickRed!30,right of=U02](U03){$(8, 3)$};
        \draw node[Vertex,fill=RoyalBlue!30,right of=U03](U04){$(6, 4)$};
        \draw node[Vertex,fill=BrickRed!30,right of=U04](U05){$(7, 5)$};
        \draw node [Vertex,fill=BrickRed!30,right of=U05](U06){$(2, 6)$};
        \draw node [Vertex,fill=RoyalBlue!30,right of=U06](U07){$(4, 7)$};
        \draw node [Vertex,fill=RoyalBlue!30,right of=U07](U08){$(1, 8)$};
        \draw [thick,->,>=latex']
        (U01.north) .. controls ($ (U01.north) + (0,2.25) $)
            and ($ (U02.north) + (0,2.25) $) .. (U02.north);
        \draw [thick,->,>=latex']
        (U04.north) .. controls ($ (U04.north) + (0,2.25) $)
            and ($ (U03.north) + (0,2.25) $) .. (U03.north);
        \draw [thick,->,>=latex']
        (U07.north) .. controls ($ (U07.north) + (0,2.5) $)
            and ($ (U05.north) + (0,2.5) $) .. (U05.north);
        \draw [thick,->,>=latex']
        (U08.north) .. controls ($ (U08.north) + (0,2.5) $)
            and ($ (U06.north) + (0,2.5) $) .. (U06.north);
    \end{tikzpicture}
    \end{split}
    \end{equation*}
    satisfying $\mathbf{P_1}$ and~$\mathbf{P_2}$.
    \smallskip

    Moreover, this shows that $\pi$ appears in the shuffle of the
    words $\textcolor{RoyalBlue}{3641}$ and
    $\textcolor{BrickRed}{5872}$, both order-isomorphic to
    $2431$.
  \end{exampleblock}
\end{frame}
